Two Monoids for Approximating \np-Complete Problems

### 2013-07-30 monoids.tex
Fixed reference to HLearn library
added reference to functor and monad structures

Before we look at implementing a \h{HomTrainer} to solve \prob{Scheduling}, we'll take a look at how it's used.
In particular, we'll look at the Haskell code I used to solve the problem of grouping my students.
In order to run the code, you'll need to download the latest \h{HLearn-approximations} library:

\begin{lstlisting}
cabal install HLearn-approximations-1.0.0
\end{lstlisting}

@@

Finally, we've looked at the monoid structure for \h{Scheduling} and \h{BinPacking}, but these types also have Abelian group and $\mathbb{Z}$-module structure as well.
I'll let you explore the documentation available on the GitHub repository \cite{hlearn} 
(pull requests are always welcome!)
to find creative ways to exploit these structures.
If you have any questions or feedback, I'd love to hear it.

>>>>

Before we look at implementing a \h{HomTrainer} to solve \prob{Scheduling}, we'll take a look at how it's used.
In particular, we'll look at the Haskell code I used to solve the problem of grouping my students.
In order to run the code, you'll need to download the latest \h{HLearn-approximation} library:

\begin{lstlisting}
cabal install HLearn-approximation-1.0.0
\end{lstlisting}

@@

Finally, we've looked at the monoid structure for \h{Scheduling} and \h{BinPacking}, but these types also have Abelian group, $\mathbb{Z}$-module, functor, and monad structure as well.
I'll let you explore the documentation available on the GitHub repository \cite{hlearn} 
(pull requests are always welcome!)
to find creative ways to exploit these structures.
If you have any questions or feedback, I'd love to hear it.
